Binocular combination in the autonomic nervous system

### 2024-04-28 manuscript.Rmd
Updated the luminance of the background
Synchronising

processdata <- 1  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data
# 2 - average data across participants, do bootstrapping
# 3 - download all raw data and analyse (requires 56GB of storage)

@@

pdf(paste(figdir,"modelfigurechap4.pdf",sep=''), bg="transparent", height = 10, width = 25)

par(mfrow=c(2,5))

params <- c(pupilRmaxLum,pupilPLum,pupilZLum,pupilWLum,pupilKLum,pupilQLum)
modresps <- getmodresps(params)

plotlims <- c(15,40,0,1)
ticklocsx <- contrastsdB    # locations of tick marks on x axis
ticklocsy <- seq(0,1,0.2)
ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
ticklabelsy <- ticklocsy

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
title(ylab="Relative amplitude at 0.5Hz", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
title(main='Luminance 1F',cex.main=2)

for (cond in 1:3){
  lines(contrastsfinedB,modresps[cond,], col=colpal[cond], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP[cond,])/abs(cleanmeansP[2,5]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
  lines(contrastsfinedB,modresps[4,], col=colpal[6], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP[6,])/abs(cleanmeansP[2,5]), pch = 25, col='black', bg=colpal[6], cex=1.6, lwd=3)   # draw the data points themselves

legend(22,1,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),pch=c(21:23,25),pt.bg=colpal[c(1:3,6)],pt.lwd=3,cex=1.5,pt.cex=1.6,box.lwd=2)
text(17,0.95,'(a)',adj=0.5,cex=2.5)

params <- c(pupilRmaxMel,pupilPMel,pupilZMel,pupilWMel,pupilKMel,pupilQMel)
modresps <- getmodresps(params)

plotlims <- c(15,40,0,1)
ticklocsx <- contrastsdB    # locations of tick marks on x axis
ticklocsy <- seq(0,1,0.2)
ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
ticklabelsy <- ticklocsy

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
title(ylab="Relative amplitude at 0.5Hz", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
title(main='Melanopsin 1F',cex.main=2)

for (cond in 1:3){
  lines(contrastsfinedB,modresps[cond,], col=colpal[cond], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP[cond,])/abs(cleanmeansP[2,5]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
  lines(contrastsfinedB,modresps[4,], col=colpal[6], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP[6,])/abs(cleanmeansP[2,5]), pch = 25, col='black', bg=colpal[6], cex=1.6, lwd=3)   # draw the data points themselves

text(17,0.95,'(b)',adj=0.5,cex=2.5)

params <- c(pupilRmaxLM,pupilPLM,pupilZLM,pupilWLM,pupilKLM,pupilQLM)
modresps <- getmodresps(params)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
title(ylab="Relative amplitude at 0.5Hz", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
title(main='L-M cones 1F',cex.main=2)

for (cond in 1:3){
  lines(contrastsfinedB,modresps[cond,], col=colpal[cond], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP[cond,])/abs(cleanmeansP[2,5]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
  lines(contrastsfinedB,modresps[4,], col=colpal[6], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP[6,])/abs(cleanmeansP[2,5]), pch = 25, col='black', bg=colpal[6], cex=1.6, lwd=3)   # draw the data points themselves

text(17,0.95,'(c)',adj=0.5,cex=2.5)

params <- c(pupilRmaxS,pupilPS,pupilZS,pupilWS,pupilKS,pupilQS)
modresps <- getmodresps(params)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
title(ylab="Relative amplitude at 0.5Hz", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
title(main='S cones 1F',cex.main=2)

for (cond in 1:3){
  lines(contrastsfinedB,modresps[cond,], col=colpal[cond], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP[cond,])/abs(cleanmeansP[2,5]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
  lines(contrastsfinedB,modresps[4,], col=colpal[6], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP[6,])/abs(cleanmeansP[2,5]), pch = 25, col='black', bg=colpal[6], cex=1.6, lwd=3)   # draw the data points themselves

text(17,0.95,'(d)',adj=0.5,cex=2.5)

# pdf(paste(figdir,"posteriors1F.pdf",sep=''), bg="transparent", height = 5.5, width = 5.5)

title(xlab="w", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
title(ylab="Probability", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
title(main='Suppression 1F',cex.main=2)

text(10,0.58,'(e)',adj=0.5,cex=2.5)

# dev.off()
# 
# pdf(paste(figdir,"posteriors2F.pdf",sep=''), bg="transparent", height = 5.5, width = 5.5)

params <- c(pupilRmaxLum2,pupilPLum2,pupilZLum2,pupilWLum2,pupilKLum2,pupilQLum2)
modresps <- getmodresps(params)

plotlims <- c(15,40,0,1)
ticklocsx <- contrastsdB    # locations of tick marks on x axis
ticklocsy <- seq(0,1,0.2)
ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
ticklabelsy <- ticklocsy

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
title(ylab="Relative amplitude at 1Hz", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
title(main='Luminance 2F',cex.main=2)

for (cond in 1:3){
  lines(contrastsfinedB,modresps[cond,], col=colpal[cond], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP2[cond,])/abs(cleanmeansP2[2,5]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
  lines(contrastsfinedB,modresps[4,], col=colpal[6], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP2[6,])/abs(cleanmeansP2[2,5]), pch = 25, col='black', bg=colpal[6], cex=1.6, lwd=3)   # draw the data points themselves

text(17,0.95,'(f)',adj=0.5,cex=2.5)

params <- c(pupilRmaxMel2,pupilPMel2,pupilZMel2,pupilWMel2,pupilKMel2,pupilQMel2)
modresps <- getmodresps(params)

plotlims <- c(15,40,0,1)
ticklocsx <- contrastsdB    # locations of tick marks on x axis
ticklocsy <- seq(0,1,0.2)
ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
ticklabelsy <- ticklocsy

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
title(ylab="Relative amplitude at 1Hz", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
title(main='Melanopsin 2F',cex.main=2)

for (cond in 1:3){
  lines(contrastsfinedB,modresps[cond,], col=colpal[cond], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP2[cond,])/abs(cleanmeansP2[2,5]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
  lines(contrastsfinedB,modresps[4,], col=colpal[6], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP2[6,])/abs(cleanmeansP2[2,5]), pch = 25, col='black', bg=colpal[6], cex=1.6, lwd=3)   # draw the data points themselves

text(17,0.95,'(g)',adj=0.5,cex=2.5)

params <- c(pupilRmaxLM2,pupilPLM2,pupilZLM2,pupilWLM2,pupilKLM2,pupilQLM2)
modresps <- getmodresps(params)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
title(ylab="Relative amplitude at 1Hz", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
title(main='L-M cones 2F',cex.main=2)

for (cond in 1:3){
  lines(contrastsfinedB,modresps[cond,], col=colpal[cond], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP2[cond,])/abs(cleanmeansP2[2,5]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
  lines(contrastsfinedB,modresps[4,], col=colpal[6], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP2[6,])/abs(cleanmeansP2[2,5]), pch = 25, col='black', bg=colpal[6], cex=1.6, lwd=3)   # draw the data points themselves

text(17,0.95,'(h)',adj=0.5,cex=2.5)

params <- c(pupilRmaxS2,pupilPS2,pupilZS2,pupilWS2,pupilKS2,pupilQS2)
modresps <- getmodresps(params)

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)     # add the tick labels
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
title(ylab="Relative amplitude at 1Hz", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
title(main='S cones 2F',cex.main=2)

for (cond in 1:3){
  lines(contrastsfinedB,modresps[cond,], col=colpal[cond], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP2[cond,])/abs(cleanmeansP2[2,5]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
}  
  lines(contrastsfinedB,modresps[4,], col=colpal[6], lwd=3, cex=0.5)
  points(contrastsdB,abs(cleanmeansP2[6,])/abs(cleanmeansP2[2,5]), pch = 25, col='black', bg=colpal[6], cex=1.6, lwd=3)   # draw the data points themselves

text(17,0.95,'(i)',adj=0.5,cex=2.5)

title(xlab="w", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
title(ylab="Probability", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
title(main='Suppression 2F',cex.main=2)

text(10,0.58,'(j)',adj=0.5,cex=2.5)

@@

coneab <- read.csv('local/coneabsorptions.csv',header=FALSE)
spectra <- read.csv('local/spectra.csv',header=FALSE)

@@

  schematic <- readTIFF('local/schematic.tiff')
  aspratio <- 15/12  # this is the aspect ratio of the output pdf
  imwidth <- 0.85
  xstart <- 0
  ystart <- 0
  rasterImage(schematic,xstart,ystart,xstart+imwidth*aspratio,ystart+imwidth)

@@

lspec <- read.csv('local/STLAB_1_oo_irrad_spectra.csv',header=FALSE)
rspec <- read.csv('local/STLAB_2_oo_irrad_spectra.csv',header=FALSE)

@@

plotlims <- c(-24,24,-24,24) 
ticklocsx <- seq(-24,24,12)    
ticklocsy <- seq(-24,24,12)      
ticklabelsx <- c('1/16','1/4','1','4','16')        
ticklabelsy <- ticklabelsx    # set labels for y ticks

@@

points(allbin[1:4,5],alldich[1:4,5],pch=21)

@@

points(allbin[5:8,5],alldich[5:8,5],pch=21)

@@

The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light [@McDougal2015]. The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size [@McDougal2008; @McDougal2015; @Wang2015]. Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil [the stimulation of one eye will cause constriction of the other eye, @Wyatt1981]. The anatomical segregation of the subcortical pathway from the rest of the brain means that this binocular combination of signals must occur independently of the cortical processes of binocular integration required for visual perception. Our recent work [@Segala2023] has shown that the algorithm underlying binocular combination of light in the pupil pathway differs from that in the cortex. Here we extend this paradigm to compare binocular combination in different photoreceptor pathways that feed into the autonomic nervous system.

@@

In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation [@Kingdom2015]. We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a high contrast dichoptic mask is shown to the other eye. In our paradigm, this mask flickered at a lower frequency (0.4Hz) so that the two stimulus components remain distinct in the Fourier spectrum [e.g. @Busse2009]. The yellow diamond symbols in Figure \@ref(fig:CRFplots) show the target responses in this condition, and in most cases are weaker than the monocular responses (red circles). The strongest dichoptic masking is found in the first harmonic L-M condition, where we also observed the binocular suppression effect. We summarise this relationship by calculating an index for each effect, and show that the binocular facilitation effect is negatively correlated with the dichoptic masking effect (see Figure \@ref(fig:suppressionfig)).

@@

Next, we fitted all 8 data sets using a Bayesian hierarchical implementation of a simple binocular combination model [@Meese2006; @Segala2023]. Our primary interest was to compare posterior distributions of the weight of interocular suppression, which are showin in Figure \@ref(fig:suppressionfig). Consistent with our earlier observations, at the first harmonic the strongest suppressive weight corresponds to the L-M condition, and the weakest suppression corresponds to the luminance condition [also consistent with @Segala2023]. The model fits were of good quality, as shown by the curves in Figure \@ref(fig:CRFplots). Further details of fitted parameters, and model behaviour in other empirical conditions are provided in the Supplementary Materials.

@@

```{r phaseplots, fig.cap="Pupil phase plots at the first and second harmonic frequencies for the luminance, melanopsin, L-M pathway and the S-(L+M) pathway conditions Panel (a) shows the pupil response at the first harmonic frequency during binocular stimulation. Panel (b) shows the pupil response at the second harmonic frequency during binocular stimulation. In panel (a) the luminance amplitudes have been scaled down by a factor of 10 to be compared with the other conditions.", fig.align="center", echo=FALSE}

@@

For all experiments, sinusoidal temporal modulations were presented against the same background spectrum (matched between the eyes), which was used to achieve silent substitution in the three photoreceptor modulation experiments. The background spectra were defined by setting all channels to half maximum output for the brighter of the two devices (STLab 1, left eye) and then using the STLab 1/STLab 2 calibration ratio to find the equivalent settings for the companion device (STLab 2, right eye). The background spectrum illuminance was approximately 74 lux, or 62 cd/m$^2$. The spectral power distributions and $\alpha$-opic irradiances of the background spectra for both eyes are shown in Figure \@ref(fig:spectraplots)c-d.

>>>>

processdata <- 3  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data
# 2 - average data across participants, do bootstrapping
# 3 - download all raw data and analyse (requires 56GB of storage)

@@

@@

coneab <- read.csv('resources/coneabsorptions.csv',header=FALSE)
spectra <- read.csv('resources/spectra.csv',header=FALSE)

@@

  schematic <- readTIFF('resources/schematic.tiff')
  aspratio <- 15/12  # this is the aspect ratio of the output pdf
  imwidth <- 0.85
  xstart <- 0
  ystart <- 0
  rasterImage(schematic,xstart,ystart,xstart+imwidth*aspratio,ystart+imwidth)

@@

lspec <- read.csv('resources/STLAB_1_oo_irrad_spectra.csv',header=FALSE)
rspec <- read.csv('resources/STLAB_2_oo_irrad_spectra.csv',header=FALSE)

@@

allfacilitation <- matrix(0,nrow=2,ncol=4)
allsuppression <- matrix(0,nrow=2,ncol=4)

allfacilitation[1,1] <- mean(modrespsLum[2,]/modrespsLum[1,])
allsuppression[1,1] <- mean(modrespsLum[1,]/modrespsLum[4,])
allfacilitation[1,2] <- mean(modrespsLM[2,]/modrespsLM[1,])
allsuppression[1,2] <- mean(modrespsLM[1,]/modrespsLM[4,])
allfacilitation[1,3] <- mean(modrespsS[2,]/modrespsS[1,])
allsuppression[1,3] <- mean(modrespsS[1,]/modrespsS[4,])
allfacilitation[1,4] <- mean(modrespsMel[2,]/modrespsMel[1,])
allsuppression[1,4] <- mean(modrespsMel[1,]/modrespsMel[4,])

allfacilitation[2,1] <- mean(modrespsLum2[2,]/modrespsLum2[1,])
allsuppression[2,1] <- mean(modrespsLum2[1,]/modrespsLum2[4,])
allfacilitation[2,2] <- mean(modrespsLM2[2,]/modrespsLM2[1,])
allsuppression[2,2] <- mean(modrespsLM2[1,]/modrespsLM2[4,])
allfacilitation[2,3] <- mean(modrespsS2[2,]/modrespsS2[1,])
allsuppression[2,3] <- mean(modrespsS2[1,]/modrespsS2[4,])
allfacilitation[2,4] <- mean(modrespsMel2[2,]/modrespsMel2[1,])
allsuppression[2,4] <- mean(modrespsMel2[1,]/modrespsMel2[4,])

plotlims <- c(1,2,1,2) 
ticklocsx <- seq(1,2,0.2)    
ticklocsy <- seq(1,2,0.2)      
ticklabelsx <- ticklocsx        
ticklabelsy <- ticklocsy    # set labels for y ticks

@@

points(allfacilitation[1,1],allsuppression[1,1],pch=21,col=stimcolours[1],bg=stimcolours[2],cex=2,lwd=3)
points(allfacilitation[1,2],allsuppression[1,2],pch=21,col=stimcolours[3],bg=stimcolours[4],cex=2,lwd=3)
points(allfacilitation[1,3],allsuppression[1,3],pch=21,col=stimcolours[6],bg=stimcolours[5],cex=2,lwd=3)
points(allfacilitation[1,4],allsuppression[1,4],pch=21,col=stimcolours[7],bg=stimcolours[8],cex=2,lwd=3)

points(allfacilitation[2,1],allsuppression[2,1],pch=22,col=stimcolours[1],bg=stimcolours[2],cex=2,lwd=3)
points(allfacilitation[2,2],allsuppression[2,2],pch=22,col=stimcolours[3],bg=stimcolours[4],cex=2,lwd=3)
points(allfacilitation[2,3],allsuppression[2,3],pch=22,col=stimcolours[6],bg=stimcolours[5],cex=2,lwd=3)
points(allfacilitation[2,4],allsuppression[2,4],pch=22,col=stimcolours[7],bg=stimcolours[8],cex=2,lwd=3)

@@

@@

The autonomic nervous system regulates many involuntary bodily processes, including the constriction and dilation of the pupils in response to light [@McDougal2015]. The anatomical pathway from the retina to the subcortical nuclei controlling the pupillary light response (PLR) is well established: it includes the Pretectal Olivary nucleus (PON), the Superior Cervical ganglion and the Edinger-Westphal nucleus, which project to the iris sphincter muscles that directly control the pupil size [@McDougal2008; @McDougal2015; @Wang2015]. Evidence of a binocular component to the PLR is shown by the existence of a consensual response of the pupil [the stimulation of one eye will cause constriction of the other eye; @Wyatt1981]. The anatomical segregation of the subcortical pathway from the rest of the brain means that this binocular combination of signals must occur independently of the cortical processes of binocular integration required for visual perception. Our recent work [@Segala2023] has shown that the algorithm underlying binocular combination of light in the pupil pathway differs from that in the cortex. Here we extend this paradigm to compare binocular combination in different photoreceptor pathways that feed into the autonomic nervous system.

@@

In contemporary models of binocular signal combination, the amount of binocular facilitation is determined by the magnitude of interocular suppression, with strong suppression reducing facilitation [@Kingdom2015]. We can estimate the strength of interocular suppression by measuring how much monocular responses are reduced when a high contrast dichoptic mask is shown to the other eye. In our paradigm, this mask flickered at a lower frequency (0.4Hz) so that the two stimulus components remain distinct in the Fourier spectrum [e.g. @Busse2009]. The yellow diamond symbols in Figure \@ref(fig:CRFplots) show the target responses in this condition, and in most cases are weaker than the monocular responses (red circles). The strongest dichoptic masking is found in the first harmonic L-M condition, where we also observed the binocular suppression effect.

@@

Next, we fitted all 8 data sets using a Bayesian hierarchical implementation of a simple binocular combination model [@Meese2006; @Segala2023]. Our primary objective was to compare posterior distributions of the weight of interocular suppression, which are shown in Figure \@ref(fig:suppressionfig). Consistent with our earlier observations, at the first harmonic the strongest suppressive weight corresponds to the L-M condition, and the weakest suppression corresponds to the luminance condition [also consistent with @Segala2023]. The model fits were of good quality, as shown by the curves in Figure \@ref(fig:CRFplots). Further details of fitted parameters, and model behaviour in other empirical conditions are provided in the Supplementary Materials. We used the model fits to summarise the relationship between binocular facilitation and interocular suppression by calculating an index for each effect, and show that the facilitation effect is negatively correlated with the dichoptic masking effect (see Figure \@ref(fig:suppressionfig)).

@@

```{r phaseplots, fig.cap="Pupil phase plots at the first and second harmonic frequencies for the luminance, melanopsin, L-M pathway and the S-(L+M) pathway conditions Panel (a) shows the pupil response at the first harmonic frequency during binocular stimulation. Panel (b) shows the pupil response at the second harmonic frequency during binocular stimulation. In panel (a) the luminance amplitudes have been scaled down by a factor of 10 to enable comparison with the other conditions.", fig.align="center", echo=FALSE}

@@

For all experiments, sinusoidal temporal modulations were presented against the same background spectrum (matched between the eyes), which was used to achieve silent substitution in the three photoreceptor modulation experiments. The background spectra were defined by setting all channels to half maximum output for the brighter of the two devices (STLab 1, left eye) and then using the STLab 1/STLab 2 calibration ratio to find the equivalent settings for the companion device (STLab 2, right eye). The background spectrum illuminance was approximately 74 lux, or 68.5 cd/m$^2$. The spectral power distributions and $\alpha$-opic irradiances of the background spectra for both eyes are shown in Figure \@ref(fig:spectraplots)c-d.
